---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  message = FALSE,
  warning = FALSE,
  collapse = TRUE,
  comment = "##",
  fig.path = "README-"
)

options(width=120)
```

# myip

Tools to Determine Your Public 'IP' Address(es)

## Description

It is often necessary to know the 'IPv4' and/or 'IPv6' external addresses of a workstation for 'API' calls. Functions are provided to use one or more external services to accomplish this task along with a wrapper function that can return results from multiple services or use a random service.

## What's Inside The Tin?

The following functions are implemented:

- `akamai`:	Use whatismyip.akamai.com to retrieve public IP address
- `amazon`:	Use checkip.amazonaws.com to retrieve public IP address
- `httpbin`:	Use httpbin.org to retrieve public IP address
- `icanhazip`:	Use icanhazip to retrieve public IP address
- `ipecho`:	Use ipecho.net/plain to retrieve public IP address
- `ipinfo`:	Use ipinfo.io/ip to retrieve public IP address
- `myip`:	Wrapper function for getting your IP address
- `opendns`:	Use checkip.dyndns.org to retrieve public IP address

## Installation

```{r eval=FALSE}
devtools::install_git("https://git.sr.ht/~hrbrmstr/myip")
# OR
devtools::install_git("https://gitlab.com/hrbrmstr/myip")
# OR
devtools::install_git("https://github.com/hrbrmstr/myip")
```

## Usage

```{r}
library(myip)

# current verison
packageVersion("myip")

akamai()

httpbin()

myip("all")
```

## myip Metrics

```{r cloc, echo=FALSE}
cloc::cloc_pkg_md()
```

## Code of Conduct

Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md). 
By participating in this project you agree to abide by its terms.
