---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```


myip is ...

The following functions are implemented:

- `akamai`:	Use whatismyip.akamai.com to retrieve public IP address
- `amazon`:	Use checkip.amazonaws.com to retrieve public IP address
- `httpbin`:	Use httpbin.org to retrieve public IP address
- `icanhazip`:	Use icanhazip to retrieve public IP address
- `ifcfgme`:	Use ifcfg.me to retrieve public IP address
- `ipecho`:	Use ipecho.net/plain to retrieve public IP address
- `ipinfo`:	Use ipinfo.io/ip to retrieve public IP address
- `myip`:	Wrapper function for getting your IP address
- `opendns`:	Use checkip.dyndns.org to retrieve public IP address
- `shuffit`:	Use shtuff.it/myip/short retrieve public IP address

### Installation

```{r eval=FALSE}
devtools::install_github("hrbrmstr/myip")
```

```{r echo=FALSE, message=FALSE, warning=FALSE, error=FALSE}
options(width=120)
```

### Usage

```{r}
library(myip)

# current verison
packageVersion("myip")

akamai()

httpbin()
```

### Test Results

```{r}
library(myip)
library(testthat)

date()

test_dir("tests/")
```

### Code of Conduct

Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md). 
By participating in this project you agree to abide by its terms.
